---
name: Tendai NR 
surname: Gwanzura
position: "PhD Candidate"
address: "Florida International University"
email: "tgwan001@fiu.edu"
github: GwanzuraT
linkedin: "/tendai-gwanzura-50380886/"
orcid: 0000-0002-2110-3530
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 414141
docname: CV
output:
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
library(tidyverse)
library(here)
library(readr)
library(scholar)
```

Highly motivated and accomplished data analyst and  early career researcher with experience in academic and government settings seeking to pivot into independent research leveraging experience in government and academic institutions.  

# Education

```{r education}

tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
    "PhD in Public Health Epidemiology", "2021-", "Florida International University", "Miami, United States",
  "Masters in Public Health", "2020", "Claremont Graduate University", "Carlifornia, United States",
  "Bachelor of Medical and Laboratory Science Honors", "2014", "University of Zimbabwe", "Harare, Zimbabwe"
) %>%
  detailed_entries(Degree, Year, Institution, Where)
```

# Professional Experience

```{r work-experience}

work_experience <- tribble(
  ~title, ~unit, ~startMonth, ~startYear, ~endMonth, ~endYear, ~where, ~detail,
  "Graduate Assistant", "Florida International University", "August", 2021, "August", 2025, "Florida International University", 
  "Collaborate with Epidemiology faculty conducting research and writing papers for peer reviewed journals.
  \\begin{itemize}
        \\item Create reports related to research being conducted and report to the Supervisor on progress.
        \\item Support students throughout their programs marking and assiting in creating lesson plans.
        \\item Collect, clean, enter and analyze data into various software application systems.
        \\item Manage data using biostatistical software such as SAS, creating weekly data reports.
    \\end{itemize}",
  
  "Data Science Fellow: Women", "Correlation One", "June", 2022, "August", 2022, "DS4A", 
  "Selected to participate in a 7-week data science Fellowship (2% acceptance rate) with learning facilitated through real-world data science business cases. 
  \\begin{itemize}
        \\item Led a group of six women to create a  model that predicted variables related to high pesticide levels in individuals 2009-2020 in the US using NHANES data, over the course of the program.
        \\item Used various regression and predictive models to complete the project utilizing python and R software.
  \\end{itemize}",
  
  "Data Science Fellow: Empowerment ", "Correlation One", "October", 2021, "December", 2022, "DS4A", 
  "Selected to participate in a 14-week data science Fellowship with a 2% acceptance rate which learning facilitated through real-world data science business cases. 
  \\begin{itemize}
        \\item Led a group of three to create a machine learning model that accurately(98%) detects brain tumors through MRI image classification, over the course of the program.
        \\item Created machine learning models to answer various business questions.
        \\item Recruited students from underrepresented groups  into the fellowship program as a DS4A ambassador.
  \\end{itemize}",
  
   "Health Program Analyst", "Los Angeles County Department of Public Health", "November", 2020, "July", 2021, "California", 
  "Collaborated with Outbreak Investigators (Public Health Nurse or Public Health Investigator) with data and epidemiology needs related to investigation of a site outbreak.
  \\begin{itemize}
        \\item Led communication with outbreak sites to conduct line list follow-up of cases and contacts, including daily monitoring.
        \\item Generated data reports related to the outbreak, including, but not limited to, epidemiological curve charts and dashboards.
        \\item Managed data collection and entry in various software application systems.
        \\item Conducted data analysis using biostatistical software such as SAS, creating weekly data reports.
  \\end{itemize}",
  
  "Data Analyst intern", "Community Translational Research Institute", "February", 2020, "June", 2020, "Claremont Graduate University", 
  "Monitored and developed data collection processes for the Diabetes Prevention Program. 
  \\begin{itemize}
        \\item Responsible for data cleaning of the electronic tracking system providing weekly reports. Removed 100% duplicate entries and 70% participant missing data filled. 
        \\item Identified and analyzed hotspots and activity spaces in Pomona Valley related to high diabetes incidence using Arc GIS.  
        \\item Performed statistical analyses using SAS and SPSS, managing large datasets, using SAS to analyze participant demographics and program outcomes. 
        \\item Coordinated with research staff in writing research papers related to the Stop Diabetes in its Tracks program outcomes. 
  \\end{itemize}",
  
  "Embryologist intern", "Bulawayo Assisted Reproductive Technology Centre", "January", 2017, "July", 2018, "Bulawayo", 
  "Performed semen analysis including sperm washing and freezing. Aided in intra uterine inseminations. 
  \\begin{itemize}
        \\item Led the quality control team of the clinic and participated in invitro fertilization procedures that entailed ova extraction and culture.
  \\end{itemize}",
  
  "Medical Laboratory Scientist", "CIMAS Medical Labs", "December", 2014, "April", 2018, "Bulawayo Harare", 
  "Performed a full range of chemical, microbiologic, immunologic, and hematological laboratory procedures.  
  \\begin{itemize}
        \\item Operated and maintained laboratory equipment also troubleshoot/resolved instrument problems. 
        \\item Led monthly and annual internal audits for accreditation.   
  \\end{itemize}"
)

```


```{r work}
work_experience %>%
  detailed_entries(
    with = title,
    what = unit,
    why = detail,
    when = glue::glue("{startMonth} {startYear} - {endMonth} {endYear}",.na = ""),
    where = where, .protect = F
  )
```

# Computer Skills

 
1. GIS Products  {ArcGIS Pro, Online, Desktop, Enterprise, Server, and App Development using Web App Builder and other software, Insights, Spatial Analysis,QGIS,KNIME} 

2. Advanced Statistical Analyses  {SAS,STATA, R, SPSS, SQL, MPlus, Python, SQL, and Tableau}  

3. Reproducible Report  {Quarto, Markdown/Rmarkdown, Jupyter Notebook} 

4. DevOps  {Git, GitHub}      

5. Microsoft  {Excel, Word, Power Point and more}  


# Academic Publications

1. Ward MK, Gwanzura T, Rojas RR, Trepka MJ, Bursac Z, Wagner EF. Nonfatal opioid-related overdoses treated by emergency medical services in Florida, before and during the COVID-19 pandemic. Preventive Medicine Reports. 2023;31:102102. doi:10.1016/j.pmedr.2022.102102
2.Chipidza W, Krewson C, Gatto N, Akbaripourdibazar E, Gwanzura T. Ideological variation in preferred content and source credibility on Reddit during the COVID-19 pandemic. Big Data & Society. 2022;9(1):20539517221076490. doi:10.1177/20539517221076486.
3. Mshigeni SK, Rittenhouse A, Gwanzura T, Arroyo R, Vaughn C. Understanding Demographics Characteristics of E-Cigarette Users in California and the Need for Tailored Interventions. American Journal of Health Education. 2021;52(4):185-193. doi:10.1080/19325037.2021.1930610
4. Chipidza W, Akbaripourdibazar E, Gwanzura T, Gatto NM. Topic Analysis of Traditional and Social Media News Coverage of the Early COVID-19 Pandemic and Implications for Public Health Communication. Disaster Medicine and Public Health Preparedness. Published online March 3, 2021:1-8. doi:10.1017/dmp.2021.65.
5. Mtetwa S, Gwanzura TNR. Interrogating Child Rights Teaching in Bindura Schools – Zimbabwe. International Journal of Educational Sciences. 2017;18(1-3):200-213. doi:10.1080/09751122.2017.1347233.
